---
title: "NHS Digital Data Checking"
author: "Ric Campbell"
date: "2021-01-27"
output: html_document
---

## Internal UoS PRIEST team only, please do not share more widely

```{r get google login access, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(data.table)
library(tinytex)
library(knitr)
library(kableExtra)
library(googlesheets4)
library(googledrive)


fn_covertStrToDate <- function(date_in, dt_format = "%Y-%m-%d") {
  date_out <- as.Date(lubridate::fast_strptime(paste(date_in, "12:00:00"), format = paste(dt_format, "%H:%M:%S"), tz = "Europe/London", lt = FALSE))
  date_out <- replace(date_out, date_out %in% as.Date("1900-01-01"), NA)
  return(date_out)
}

fn_removeBlanks <- function(field) {
  field <- trimws(field)
  return(replace(field, field == "", NA))
}


## Give script permission to use auth token found in cache

warning("You must have connected to your Google account proir to running this script as it uses the auth token found in the cache")
# gs4_auth() - may need re-doing even if have not shut down RStudio
# Then run markdown from console:
# rmarkdown::render("RMarkdown/nhs_digital_data_checking_and_outputs.Rmd")

options(gargle_oauth_email = TRUE)

```

```{r, echo = FALSE}

## Read in all data from NHS Digital

apc1 <- fread("D:/source_data/nhs_digital/apc/NIC377644_HES_APC_201999_APPROVED_51667_01010001_0.txt", colClasses = "character")
apc2 <- fread("D:/source_data/nhs_digital/apc/NIC377644_HES_APC_202006_APPROVED_51668_01010001_0.txt", colClasses = "character")

apc <- rbind(apc1, apc2)


critical_care1 <- fread("D:/source_data/nhs_digital/cc/NIC377644_HES_CC_201999_APPROVED_51669_01010001_0.txt", colClasses = "character")
critical_care2 <- fread("D:/source_data/nhs_digital/cc/NIC377644_HES_CC_202006_APPROVED_51670_01010001_0.txt", colClasses = "character")

critical_care <- rbind(critical_care1, critical_care2)


demographic <- fread("D:/source_data/nhs_digital/demo/FILE0115974_NIC377644_Demographics__APPROVED_53999_01010001_0.txt", colClasses = "character")

death_reg <- fread("D:/source_data/nhs_digital/dr/FILE0115975_NIC377644_CIVREG_MORT__APPROVED_54000_01010001_0.txt", colClasses = "character")


ecds1 <- fread("D:/source_data/nhs_digital/ecds/NIC377644_ECDS_201999_APPROVED_51664_01010001_0.txt", colClasses = "character")
ecds2 <- fread("D:/source_data/nhs_digital/ecds/NIC377644_ECDS_202006_APPROVED_51665_01010001_0.txt", colClasses = "character")

ecds <- rbind(ecds1, ecds2)

gdppr <- fread("D:/source_data/nhs_digital/gdppr/NIC377644_GDPPR_20201204_APPROVED_51666_01010001_0.txt", colClasses = "character")


rm(apc1, apc2, critical_care1, critical_care2, ecds1, ecds2)


# Convert date fields to dates

apc[, ADMIDATE := fn_covertStrToDate(ADMIDATE)]
critical_care[, EPISTART := fn_covertStrToDate(EPISTART)]
death_reg[, DATE_OF_DEATH := fn_covertStrToDate(REG_DATE_OF_DEATH, dt_format = "%Y%m%d")]
death_reg[, REG_DATE_OF_DEATH := NULL]
ecds[, ARRIVAL_DATE := fn_covertStrToDate(ARRIVAL_DATE)]
gdppr[, DATE := fn_covertStrToDate(DATE)]


## Read in col names that we asked for from Google Sheet

nhs_digital_requested_data <- as.character(as_sheets_id("https://docs.google.com/spreadsheets/d/1ONAYEbbd_dfwqfy-D0jrOeP31pem-gFytsyojfwrp1o/edit#gid=1397121393"))


## Read in sites sheet from google drive - correctly formatted field name has been done

## Might have to put a delay in as too many read requests in short space of time?

 suppressMessages(apc_requested <- data.table(range_read(nhs_digital_requested_data,
                                       sheet = "APC", col_types = "c")))

 suppressMessages(cc_requested <- data.table(range_read(nhs_digital_requested_data,
                                        sheet = "CC", col_types = "c")))

 suppressMessages(demo_requested <- data.table(range_read(nhs_digital_requested_data,
                                        sheet = "DEMO", col_types = "c")))

 suppressMessages(dr_requested <- data.table(range_read(nhs_digital_requested_data,
                                        sheet = "DR", col_types = "c")))

 suppressMessages(ecds_requested <- data.table(range_read(nhs_digital_requested_data,
                                       sheet = "ECDS", col_types = "c")))
 
 suppressMessages(gdppr_requested <- data.table(range_read(nhs_digital_requested_data,
                                       sheet = "GDPPR", col_types = "c")))


## Change all col names to upper case and take col names and change one to correct data dictionary label

apc_colnames <- colnames(setnames(apc, colnames(apc), toupper(colnames(apc))))
cc_colnames <- colnames(setnames(critical_care, colnames(critical_care), toupper(colnames(critical_care))))
demo_colnames <- colnames(setnames(demographic, colnames(demographic), toupper(colnames(demographic))))
dr_colnames <- colnames(setnames(death_reg, colnames(death_reg), toupper(colnames(death_reg))))
ecds_colnames <- colnames(setnames(ecds, colnames(ecds), toupper(colnames(ecds))))
gdppr_colnames <- colnames(setnames(gdppr, colnames(gdppr), toupper(colnames(gdppr))))

setnames(apc, "PROVSPNOPS", "PROVSPNO")


## Make changes to requested list to add entries that have multiple fields

## APC - number of fields that should be present taken from data dictionary

apc_requested_names <- c(apc_requested[field_name != "DEPDAYS_N" & field_name !="DIAG_4_NN" & field_name != "INTDAYS_N", field_name],
                         paste0("DEPDAYS_", 1:9), paste0("DIAG_4_", formatC(1:20, width = 2, format = "d", flag = "0")), paste0("INTDAYS_", 1:9))


## ECDS - number of fields that should be present created to match up with data provided
## All fields have a group (or field) repeat of 1...* as found in the technical output specification (V3.0) available on NHS Digital website

ecds_requested_names <- c(ecds_requested[field_name != "COMORBIDITIES" & field_name != "DIAGNOSIS_CODE" & field_name != "DIAGNOSIS_QUALIFIER"
                                         & field_name != "INVESTIGATION_CODE" & field_name != "REFERRED_TO_SERVICE" & field_name != "SEQUENCE_NUMBER"
                                         & field_name != "TREATMENT_CODE", field_name],
                          paste0("COMORBIDITIES_", 1:10), paste0("DIAGNOSIS_CODE_", 1:12), paste0("DIAGNOSIS_QUALIFIER_", 1:12),
                          paste0("INVESTIGATION_CODE_", 1:12), paste0("REFERRED_TO_SERVICE_", 1:4), paste0("SEQUENCE_NUMBER_", 1:12),
                          paste0("TREATMENT_CODE_", 1:12))


## Keep only the non-code cols names for gdppr 
 
  gdppr_requested_names <- unique(gdppr_requested[, is_code_list := 
                                             substr(field_name, nchar(field_name)-3, nchar(field_name)) == "_COD"][is_code_list == FALSE, field_name])


## Check that we have received all the cols asked for, and if have received any more

  missing_apc_cols <- apc_requested_names[!apc_requested_names %in% apc_colnames]
  extra_apc_cols <- apc_colnames[!apc_colnames %in% apc_requested_names]
  
  missing_cc_cols <- cc_requested[!cc_requested[, toupper(field_name)] %in% cc_colnames][, toupper(field_name)]
  extra_cc_cols <- cc_colnames[!cc_colnames %in% cc_requested[, toupper(field_name)]]
  
  missing_demo_cols <- demo_requested[!demo_requested[, field_name] %in% demo_colnames][, field_name]
  extra_demo_cols <- demo_colnames[!demo_colnames %in% demo_requested[, field_name]]
   
  missing_dr_cols <- dr_requested[!dr_requested[, field_name] %in% dr_colnames][, field_name]
  extra_dr_cols <- dr_colnames[!dr_colnames %in% dr_requested[, field_name]]
  
  missing_ecds_cols <- ecds_requested_names[!ecds_requested_names %in% ecds_colnames]
  extra_ecds_cols <- ecds_colnames[!ecds_colnames %in% ecds_requested_names]
  
  missing_gdppr_cols <- gdppr_requested_names[!gdppr_requested_names %in% gdppr_colnames]
  extra_gdppr_cols <- gdppr_colnames[!gdppr_colnames %in% gdppr_requested_names]



## Look if any data is in the extra cols provided for either demographics or death register - first replace blanks with NA
  
  demographic[, (demo_colnames) := lapply(.SD, fn_removeBlanks), .SDcols = demo_colnames]
  death_reg[, (dr_colnames) := lapply(.SD, fn_removeBlanks), .SDcols = dr_colnames]
  

  demo_non_na_count <- t(demographic[, lapply(.SD, function(x) sum(!is.na(x))), .SDcols = extra_demo_cols])

  death_reg_non_na_count <- t(death_reg[, lapply(.SD, function(x) sum(!is.na(x))), .SDcols = extra_dr_cols])


# ## Limit APC data to just the Study ids we have in demo dataset as demo is being used as out single source of truth
# 
#   demo_study_ids <- demographic[, STUDY_ID]
# 
#   apc_demo_only <- apc[STUDY_ID %in% demo_study_ids]


## Find number of unique records, unique study_ids (or similar) for each dataset before building table

# ### APC
# 
#   apc_records <- length(apc_demo_only[!is.na(EPIKEY), unique(EPIKEY)])
#   apc_people_soft <- length(apc_demo_only[!is.na(ENCRYPTED_HESID), unique(ENCRYPTED_HESID)])
#   apc_study_ids <- length(apc_demo_only[!is.na(STUDY_ID), unique(STUDY_ID)])

  ## Numbers just for APC whiled do not have Demo dataset - still using as would involve doing the whole identifying here

  apc_records <- length(apc[!is.na(EPIKEY), unique(EPIKEY)])
  apc_people_soft <- length(apc[!is.na(ENCRYPTED_HESID), unique(ENCRYPTED_HESID)])
  apc_study_ids <- length(apc[!is.na(STUDY_ID), unique(STUDY_ID)])


### CC
 ## Find all APC records that have a SUSRECID from CC, to find numbers for critical care

  all_cc_susrecids <- critical_care[, unique(SUSRECID)]
 
  # cc_apc_sub_cohort <- apc_demo_only[SUSRECID %in% all_cc_susrecids]
   
  cc_apc_sub_cohort <- apc[SUSRECID %in% all_cc_susrecids]

 
 ## Check if have an APC record for every Critical Care record

   stopifnot(length(setdiff(all_cc_susrecids, apc[, unique(SUSRECID)])) == 0)


  ## How many do not have an APC record as have removed APC records not recorded in the demo dataset

  #  cc_records_not_from_demo_trace <- length(setdiff(all_cc_susrecids, cc_apc_sub_cohort[, unique(SUSRECID)]))


  # ## Find numbers for critical care
  # 
  #   cc_records <- length(all_cc_susrecids)
  #   cc_people_soft <- length(cc_apc_sub_cohort[!is.na(ENCRYPTED_HESID), unique(ENCRYPTED_HESID)])
  #   cc_study_ids <- length(cc_apc_sub_cohort[!is.na(STUDY_ID), unique(STUDY_ID)])

  ## Numbers for CC while we don't have Demo dataset - keeping this as don't want to do all identifying of patient here

     cc_records <- length(all_cc_susrecids)
     cc_people_soft <- length(cc_apc_sub_cohort[!is.na(ENCRYPTED_HESID), unique(ENCRYPTED_HESID)])
     cc_study_ids <- length(cc_apc_sub_cohort[!is.na(STUDY_ID), unique(STUDY_ID)])


### Demographics

 demo_records <- unique(demographic)[, .N]
 demo_people_soft <- length(demographic[!is.na(NHS_NO), unique(NHS_NO)])
 demo_study_ids_count <- length(demographic[!is.na(STUDY_ID), unique(STUDY_ID)])


### Death register

 death_records <- unique(death_reg)[, .N]
 death_people_soft <- length(death_reg[!is.na(DEC_CONF_NHS_NUMBER), unique(DEC_CONF_NHS_NUMBER)])
 death_study_ids <- length(death_reg[!is.na(STUDY_ID), unique(STUDY_ID)])
    
    
### EDCS
    
  ecds_records <- unique(ecds)[, .N]
  ecds_people_soft <- length(ecds[!is.na(NHS_NUMBER), unique(NHS_NUMBER)])
    
    
### GDPPR
    
  gdppr_records <- unique(gdppr)[, .N]
  gdppr_people_soft <- length(gdppr[!is.na(NHS_NUMBER), unique(NHS_NUMBER)])
  gdppr_study_ids <- length(gdppr[!is.na(STUDY_ID), unique(STUDY_ID)])
    

## Create table with numbers of rows, distinct records, unique study_ids, min/max dates

    dataset_numbers <- data.table(dataset = "APC", number_of_rows = apc[, .N], number_of_records = apc_records, 
                                  rough_number_of_people = apc_people_soft, number_study_ids = apc_study_ids,
                                  min_date = as.character(apc[!is.na(ADMIDATE), min(ADMIDATE)]),
                                  max_date = as.character(apc[!is.na(ADMIDATE), max(ADMIDATE)]))
    
    dataset_numbers <- rbind(dataset_numbers, list("Critical Care", critical_care[, .N], cc_records, cc_people_soft, cc_study_ids,
                                                   as.character(critical_care[!is.na(EPISTART), min(EPISTART)]),
                                                   as.character(critical_care[!is.na(EPISTART), max(EPISTART)])))
    
    dataset_numbers <- rbind(dataset_numbers, list("Demographics", demographic[, .N],
                                                   demo_records, demo_people_soft, demo_study_ids_count, NA, NA))
                                                   
     
    dataset_numbers <- rbind(dataset_numbers, list("Death Register", death_reg[, .N],
                                                   death_records, death_people_soft, death_study_ids,
                                                   as.character(death_reg[!is.na(DATE_OF_DEATH), min(DATE_OF_DEATH)]),
                                                   as.character(death_reg[!is.na(DATE_OF_DEATH), max(DATE_OF_DEATH)])))
    
    dataset_numbers <- rbind(dataset_numbers, list("ECDS", ecds[, .N], ecds_records, ecds_people_soft, NA,
                                                   as.character(ecds[!is.na(ARRIVAL_DATE), min(ARRIVAL_DATE)]),
                                                   as.character(ecds[!is.na(ARRIVAL_DATE), max(ARRIVAL_DATE)])))
    
    dataset_numbers <- rbind(dataset_numbers, list("GDPPR", gdppr[, .N], gdppr_records, gdppr_people_soft, gdppr_study_ids,
                                                   as.character(gdppr[!is.na(DATE) & DATE > "1900-01-01", min(DATE)]),
                                                   as.character(gdppr[!is.na(DATE), max(DATE)])))
    
```

# Comparison of the coloumns that we asked for and we have received for NHS Digital datasets

Missing APC columns: `r paste0(missing_apc_cols, collapse = " ")`  
Extra APC columns: `r paste0(extra_apc_cols, collapse = " ")`  

Missing Critical Care columns: `r paste0(missing_cc_cols, collapse = " ")`  
Extra Critical Care columns: `r paste0(extra_cc_cols, collapse = " ")`

Missing ECDS columns: `r paste0(missing_ecds_cols, collapse = " ")`  
Extra ECDS columns: `r paste0(extra_ecds_cols, collapse = " ")`

Number of missing columns in demographic dataset: `r length(missing_demo_cols)`
Number of extra columns in demographic dataset: `r length(extra_demo_cols)`

Number of missing columns in death register dataset: `r length(missing_demo_cols)`
Number of extra columns in death register dataset: `r length(extra_demo_cols)`

Missing GDPPR columns: `r paste0(missing_gdppr_cols, collapse = " ")`  
Extra GDPPR columns: `r paste0(extra_gdppr_cols, collapse = " ")`\


```{r, echo = FALSE}

# paste0(c("Missing APC coloumns: ", missing_apc_cols), collapse = " ")
# paste0(c("Extra APC coloumns: ", extra_apc_cols), collapse = " ")
# 
# paste0(c("Missing CC coloumns: ", missing_cc_cols), collapse = " ")
# paste0(c("Extra CC coloumns: ", extra_cc_cols), collapse = " ")
# 
# paste0("Number of missing coloumns in demographic dataset: ", length(missing_demo_cols))
# paste0("Number of extra coloumns in demographic dataset: ", length(extra_demo_cols))
# 
# paste0("Number of missing coloumns in death register dataset: ", length(missing_demo_cols))
# paste0("Number of extra coloumns in death register dataset: ", length(extra_demo_cols))

```

# Table showing the the extra coloumns in demographic dataset, and the number of rows that are not blank

```{r, echo = FALSE}
kable_styling(kable(demo_non_na_count), full_width = FALSE)

```

# Table showing the the extra coloumns in death register dataset, and the number of rows that are not blank

```{r, echo = FALSE}
kable_styling(kable(death_reg_non_na_count), full_width = FALSE)

```

# Summary of the data received from NHS Digital

```{r, echo = FALSE}
kable_styling(kable(dataset_numbers, format = "html"))

```

<!-- # Number of Study IDs present in Critical Care dataset that are not found in demographic dataset -->

```{r, echo = FALSE}
#cc_records_not_from_demo_trace

```

